---
title: "starckc5"
author: "Camille Starck"
date: "4/5/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# Required Packages:
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org") # We need this for read_csv
```

## Introduction

An insurance company has 1,000 policies that each have a premium of $2,000. There is a 1.5% chance that a claim will be made for a life insurance payout of $1,000,000. We use a simulation with 10,000 examples to show the company what earnings on each policy might look like for a typical year, and decide whether or not the premium is high enough.


## Analysis 
Here we set up the simulation of 10,000 example years with 1,000 policies per year. 
```{r , echo=TRUE}
# Possible outcomes for each policy
x <- c(2000, -998000) 

# Simulation
allYears <- replicate(10000, { # 10000 examples
  # outcomes of 1000 policies
  sampleYear <- sample(x, 1000, prob=c(.985,.015), replace = TRUE) 
  # net profit of all the 1000 policies
  sum(sampleYear) } ) 


```


The net profit per year is calculated by summing the earnings of all 1,000 policies. 
The following are a few sample net profits of the 10,000 example years. 
```{r , echo=FALSE}
# Display the first few net profits of the 10,000 examples

head(allYears)
# average yearly earnings on 1000 policies
```
Next, we calculate the average yearly earnings on 1,000 policies.
```{r , echo=FALSE}
sum(allYears)/10000 
```
Finally, we calculate the expected earnings per policy.
```{r , echo=FALSE}
2000*.985 + (2000-1000000)*.015
```

## Visualization

```{r , echo=FALSE}
# Histogram
h <- as.data.frame(allYears) %>% ggplot()
h + geom_histogram(aes(x=allYears), fill='lightskyblue', col = 'black', bins=15) + 
  labs(title='Negative Net Profit of 10,000 Insurance Policies',
       x = 'Net Profit') + 
  scale_x_continuous(labels = scales :: dollar_format())
```

## Conclusion
From the histogram and the analysis, we can see that in a simulation with 10,000 example years and 1,000 policies per year, the insurance company will consistently lose money. More often than not, the company will lose millions of dollars per year. The company should increase the premium to avoid negative net profit.  